Minimax lower bounds for source localization

### 2017-01-05 paper.tex
Make fixes to caption, add new figure.

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}

@@

We now state the main result of this paper.
\begin{theorem}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the minimax risk in estimating the location of a
	point source is lower bounded by:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=2.8in]{overlap-middle-pics}
	\caption{Depiction of the impulse responses corresponding to two
	hypotheses, $\theta_0$ and $\theta_1$. Note that each impulse response has
a support of size $w$, and the two are separated by a distance $2\delta$. The
total size of the support of the difference signal (subtracting one impulse
response from the other, pointwise) $\Delta(t)$ is therefore at most $w +
2\delta$.}
	\label{fig:overlap-middle}
\end{figure}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
%\usepackage{caption}
%\usepackage{subcaption}

%\captionsetup[figure]{textfont=footnotesize,labelfont=footnotesize}

@@

We now state the main result of this paper.
\begin{theorem}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the asymptotic minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=2.8in]{overlap-middle-pics}
	\caption{Depiction of the continuous-space signals produced by two
		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
		shifted impulse response, and therefore has a support of size $w$.
		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
		$\Theta$, so the signals are separated by a distance $2\delta$.}
	\label{fig:overlap-middle}
\end{figure}

\begin{figure}[tbp]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}
